---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# oeis

<!-- badges: start -->
<!-- badges: end -->

The goal of oeis is to provide access to integer sequences from http://oeis.org and some to include some helper functions to ease analysis on the sequences.

## Installation

You can install the development version with:

```
install.packages("remotes")
remotes::install_github("jpmarindiaz/oeis")
```

## List and get OEIS sequences



List all available sequences with `sequences`

```{r}
library(oeis)

head(sequences)

```

Search for a sequence by some term in the sequence description.

```
search_sequence("prime numbers")
# Returns 973 sequences with "prime numbers" in the description
```


Download a sequence

```{r}
a1 <- get_sequence("A306302")
a2 <- get_sequence("A331766")
#a3 <- get_sequence("A999999") # Error. Sequence not in catalog.
```

## Fitting models to sequences

TODO
Work in progress!


```{r fit}
# Fit polynomials
# Find best polynomial order
```

